### 2016-01-14 Projects/DelCo_2014_2015/Report/Hose_Stream_Report/TeX_Files/DelCo_Hose_Tests_2014.tex
DelCo_2014 and DelCo_2015 combined into one directory

\begin{figure}[!ht]
\includegraphics[width=6in]{../Drawings/West_Test_Structure_2nd_Floor_Dimensioned}
\includegraphics[width=6in]{../Drawings/West_Test_Structure_1st_Floor_Dimensioned}
\caption[Plan view of the second floor and first floor of the West Structure.]{Plan view of the first floor (top) and second floor (bottom) of the West Structure.}
\label{fig:west_general_plan}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_18_1st_Floor_Annotated}
\caption[Plan view of the West Structure setup for Tests 16 and 18.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 16 and 18. The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A10 (blue square). On the second floor, the stairwell door and north side, west double door were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
\label{fig:flow_path_1}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_19_1st_Floor_Annotated}
\caption[Plan view of the West Structure setup for Tests 17 and 19.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 17 and 19. The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A10 (blue square). On the second floor, the stairwell door and north side, west double door were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
\label{fig:flow_path_2}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_16_West_063014_custom_BDP_A10_Avg}
\caption{Average velocity measured by the BDPs at A10 during Test 16 for three hose stream patterns.}
\label{fig:Test_16_BDP_A10_Avgs}
\end{figure}
\FloatBarrier

@@

\begin{table}[!ht]
\caption{Average air velocity (m/s) through interior doorway when flow path was fully established for each monitor experiment}
\begin{tabular}{lccccc}
\toprule
 & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}} & \underline{Test 33}
\\
% \textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} 
\textbf{Stream} & 
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South Doorway} \\ \end{tabular}
\\ 
\midrule
\textit{Straight} & 0.9 $\pm0.1$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.2$ & -0.3 $\pm0.1$
\\ \multicolumn{6}{c}{} \\
\textit{Narrow Fog} & 0.9 $\pm0.2$ & 1.4 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.1$ & 1.0 $\pm0.6$
\\ \multicolumn{6}{c}{} \\
\textit{Wide Fog} & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.2$ & 2.4 $\pm0.3$
\\ \bottomrule
\end{tabular}
\label{table:all_mon_vel_avgs}
\end{table}
\FloatBarrier

@@

%\begin{figure}[!ht]
%\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg_CW_vs_CCW}
%\caption{Average Velocity of Stairwell Door, Test 18, All Streams, CW vs. CCW}
%\label{fig:Test_18_BDP_A10_Avg_CW_vs_CCW}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg_CW_vs_CCW}
%\caption{Average Velocity of Stairwell Door, Test 19, All Streams, CW vs. CCW}
%\label{fig:Test_19_BDP_A10_Avg_CW_vs_CCW}
%\end{figure}
%
%\clearpage

@@

>>>>

\begin{figure}[!ht]
\includegraphics[width=6in]{../Drawings/West_Test_Structure_2nd_Floor_Dimensioned}
\\~\\
\includegraphics[width=6in]{../Drawings/West_Test_Structure_1st_Floor_Dimensioned}
\caption[Plan view of the second floor and first floor of the West Structure.]{Plan view of the second floor (top) and first floor (bottom) of the West Structure.}
\label{fig:west_general_plan}
\end{figure}

@@

\begin{figure}[!ht]
\
\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
\\~\\
\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_18_1st_Floor_Annotated}
\caption[Plan view of the West Structure setup for Tests 16 and 18.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 16 and 18. The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A10 (blue square). On the second floor, the stairwell door and north side, west double door were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
\label{fig:flow_path_1}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
\\~\\
\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_19_1st_Floor_Annotated}
\caption[Plan view of the West Structure setup for Tests 17 and 19.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 17 and 19. The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A10 (blue square). On the second floor, the stairwell door and north side, west double door were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
\label{fig:flow_path_2}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_16_West_063014_BDP_A10_stream_avgs}
\caption{Average velocity measured by the BDPs at A10 during Test 16 for three hose stream patterns.}
\label{fig:Test_16_BDP_A10_Avg_All}
\end{figure}
\FloatBarrier

@@

\begin{table}[!ht]
\caption{Average air velocity (m/s $\pm15$\%) through interior doorway when flow path was fully established for each monitor experiment}
\begin{tabular}{lccccc}
\toprule
 & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}} & \underline{Test 33}
\\
% \textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} 
\textbf{Stream} & 
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South Doorway} \\ \end{tabular}
\\ 
\midrule
\textit{Straight} & 0.9 $\pm0.1$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.2$ & -0.3 $\pm0.1$
\\ \multicolumn{6}{c}{} \\
\textit{Narrow Fog} & 0.9 $\pm0.2$ & 1.4 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.1$ & 1.0 $\pm0.6$
\\ \multicolumn{6}{c}{} \\
\textit{Wide Fog} & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.2$ & 2.4 $\pm0.3$
\\ \bottomrule
\end{tabular}
\label{table:all_mon_vel_avgs}
\end{table}
\FloatBarrier

@@

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A10_stream_avgs}
\caption{Average velocity measured by the BDPs at A10 during Test 17 for three hose stream patterns.}
\label{fig:Test_17_BDP_A10_Avg_All}
\end{figure}
\FloatBarrier

### 2016-01-14 Projects/DelCo_2014_2015/Report/hose_report.tex
DelCo_2014 and DelCo_2015 combined into one directory

\usepackage{parskip} % Adds spacing between paragraphs
\usepackage{hyperref}
\frenchspacing
\setlength{\parindent}{15pt} % Indent paragraphs

\hypersetup{colorlinks=true, urlcolor=blue, citecolor=black, linkcolor=blue}

@@

\memofrom{Daniel Madrzykowski \\ Craig Weinschenk \\ NIST Firefighting Technology Group} % Sender(s)

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.45\columnwidth]{../Figures/Hose_Figures/exterior_a}
\includegraphics[width=0.45\columnwidth]{../Figures/Hose_Figures/exterior_c}
\caption{Photographs of Side A (Left) and Side C (Right). }
\label{fig:exterior}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.8\columnwidth]{../Figures/Hose_Figures/test_setup_1b}
\caption{Locations of instrumented hose samples relative to the vertical thermocouple array, the heat flux gauge and the radiometer.}
\label{fig:test_setup_1b}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.8\columnwidth]{../Figures/Hose_Figures/test_plan}
\caption{Schematic showing the test arrangement on the lower level. The circle represents the thermocouple array, the diamond represents the heat flux gauge and radiometer, and the squares represent the bi-directional velocity probes in the open doorway on Side C.}
\label{fig:test_plan}
\end{figure}

@@

>>>>

\usepackage{parskip} % Adds spacing between paragraphs
\usepackage{hyperref}
\frenchspacing
\setlength{\parindent}{15pt} % Indent paragraphs
\usepackage{color}
\newcommand{\white}[1]{{\textcolor{white}{#1}}}
\hypersetup{colorlinks=true, urlcolor=blue, citecolor=black, linkcolor=blue}

@@

\memofrom{Daniel Madrzykowski \\ \white{s:}Craig Weinschenk \\ \white{s:}NIST Firefighting Technology Group} % Sender(s)

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.45\columnwidth]{../Figures/Hose_Figures/exterior_a}
\includegraphics[width=0.45\columnwidth,trim = 1.25in 1.5in .75in 0in, clip=true,]{../Figures/Hose_Figures/exterior_c}
\caption{Photographs of Side A (Left) and Side C (Right). }
\label{fig:exterior}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.8\columnwidth,angle =-90]{../Figures/Hose_Figures/test_setup_1b}
\caption{Locations of instrumented hose samples relative to the vertical thermocouple array, the heat flux gauge and the radiometer.}
\label{fig:test_setup_1b}
\end{figure}

@@

% \begin{figure}[!ht]
% \centering
% \includegraphics[width=.8\columnwidth]{../Figures/Hose_Figures/test_plan}
% \caption{Schematic showing the test arrangement on the lower level. The circle represents the thermocouple array, the diamond represents the heat flux gauge and radiometer, and the squares represent the bi-directional velocity probes in the open doorway on Side C.}
% \label{fig:test_plan}
% \end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.8\columnwidth]{../Figures/Hose_Figures/IMG_8431}
\caption{Photograph as the fire room transitioned to flashover in Experiment 2.}
\label{fig:flashover}
\end{figure}
